Syntax and Semantics of Abstract Binding Trees

### 2015-11-09 paper.tex
fix typo (presheaf -> copresheaf)

The only place that symbols appear in our calculus is as parameters to
operators (unlike variables, symbols are not terms). Therefore, the functorial
action of the operator presheaf can be lifted into terms by recursion on their
structure, via a pair of judgments $\IsRenaming{\varrho}{M}{N}$ and
$\IsRenaming{\varrho}{E}{F}$, presupposing
$\Of{\varrho}{\Upsilon\to\Upsilon'}$, and $\IsAbt{\Omega}{\Upsilon}{\Gamma}{M}{\tau}$
and $\IsAbt{\Omega}{\Upsilon}{\Gamma}{E}{v}$ respectively:

>>>>

The only place that symbols appear in our calculus is as parameters to
operators (unlike variables, symbols are not terms). Therefore, the functorial
action of the operator copresheaf can be lifted into terms by recursion on their
structure, via a pair of judgments $\IsRenaming{\varrho}{M}{N}$ and
$\IsRenaming{\varrho}{E}{F}$, presupposing
$\Of{\varrho}{\Upsilon\to\Upsilon'}$, and $\IsAbt{\Omega}{\Upsilon}{\Gamma}{M}{\tau}$
and $\IsAbt{\Omega}{\Upsilon}{\Gamma}{E}{v}$ respectively:
